### 2018-12-14 Chapters/Chapter2.tex
added hubbard discussion

Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the Hubbard model that we will use in the next sections:

@@

>>>>

Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the model that we will use in the next sections:

@@

\begin{subsection}{Hubbard model}

In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$. This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}. Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it. Originally the Hubbard model was proposed to describe electron correlations in a simplified way and to predict metal-insulator transitions. It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory. Also, the attractive Hubbard model (where $\text{U} < 0$) is relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.

\end{subsection}
